Analyzing The National's Musical Trajectory from 2001 to 2023

### 2024-10-10 paper/paper.qmd
styler

---
title: "Rush hour subways surprisingly excel at punctuality: a closer look at TTC Delays"
subtitle: "Insight into when delays disproportionately tend to happen and related statistics"
author: 
  - Andrew Goh, Yisu Hou, Jiwon Choi
thanks: "Code and data are available at: https://github.com/mushroomcarbon/TTCDelays."
date: today
date-format: long
abstract: "This paper uses data from Open Data Toronto on TTC subway and bus
delays to analyze how the delays are generally distributed w.r.t. the time of day. Mean, total, and adjusted statistics were graphed, leading to the conclusions that subways are almost always
more punctual than buses, peak hour leads to the fewest delays, and leaving 10-15 minutes earlier is a safe margin of error for delays. The conclusions of this paper provide a practical, actionable set of guidelines on how citizens can ensure/maximize punctuality when using the TTC to go about the city, as well as potential insight into where resources can be invested in to increase TTC efficiency the most."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{placeins}
---

@@

The R programming language (@talia), dplyr (@dplyr), opendatatoronto(@opendatatoronto), and tidyverse(@thereferencecanbewhatever) were used to download, modify, and analyse data obtained from Open Data Toronto. Styler (@styler) was used to style the code. Data used in this paper comes from the "TTC Subway Delays" (@subway_data) and "TTC Bus Delays" (@bus_data) data sets from the Open Data Toronto database, published by the TTC.

@@

# Load the data
data <- read_rds(here::here("data/the_national.rds"))

>>>>

---
title: "Analyzing The National's Musical Trajectory from 2001 to 2023"
subtitle: "A Spotify Data Analysis of Danceability, Energy, Instrumentalness, and Valence Trends"
author: 
  - Andrew Goh, Yisu Hou, Jiwon Choi, Xiaolu Ji
thanks: "Code and data are available at: https://github.com/mushroomcarbon/Spotify."
date: today
date-format: long
abstract: "This study analyzes the evolution of musical attributes in The National’s discography, focusing on danceability, energy, instrumentalness, and valence across their album releases. Using data from Spotify’s API, we analyze how these attributes have fluctuated over the years and visualize their progression through a series of plots. Our findings suggest that energy and instrumentalness exhibit more variability, while danceability and valence have followed relatively smoother trajectories. These insights contribute to the growing field of music analytics by offering a deeper understanding of the artistic and sonic evolution of a famous band within the indie rock genre."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{placeins}
---

@@

The R programming language [@talia], dplyr [@dplyr], tidyverse[@thereferencecanbewhatever] were used to download, modify, and analyse data obtained from Spotify [@spotify_api] using the SpotifyR package [@spotifyr] regarding music from The National [@the_national]. Styler [@styler] was used to style the code.

@@

# Load the data
data <- read_rds(here::here("data/analysis_data/the_national_cleaned.rds"))
